Order reduction and partial MILP models \\ for certifying Robustness of DNNs globally.

### 2025-07-26 AAAI2026/Lipitschz.tex
intro (from ATVA)
abstract

In this paper, we consider global robustness, that is guarantees on robustness irrespective of a (set of) local images.
For that, we consider the switch of values between the different decision classes of a DNN due to a given perturbation. 
The verification question is much more complex, as the number of complex variables doubles (from the deviation image to the image and its deviation).
Further, the values each neuron can take is no more in a small neighborhood. 
Therefore, the global verification process becomes much harder.
To obtain useable bounds, we use the most accurate process to date, 
using partial MILP (pMILP) methodology. 
We propose several such pMILP models for global robustness, with different trade-offs.
Last, we use order reduction techniques to reduce the space of image considered, 
avoiding unrealistic inputs, by using linear PCA. 
This results into usable bounds, allowing in real time to certify robustness for $>87\%$ of incoming images 
in the MNIST benchmark for a L1 perturbation of $\frac{1}{2}$, as well as for a surrogate computing the hidden plastic strain 
associated to a deformation map of a pipe.
	\end{abstract}

@@

	%\input{introduction}

>>>>

In this paper, we consider {\em global} robustness, that is guarantees on robustness not restricted to a set of local images.
For that, we consider the switch of values between the different decision classes of a DNN due to a given perturbation. 
The verification question is much more complex, as the number of complex variables doubles (from the deviation image to the image and its deviation).
Further, the values each neuron can take is no more in a small neighborhood. 
Therefore, the global verification process becomes much harder.
To obtain useable bounds, we use the most accurate process to date, 
using partial MILP (pMILP) methodology. 
We propose several such pMILP models for global robustness, with different trade-offs.
Last, we use order reduction techniques to reduce the space of image considered, 
avoiding unrealistic inputs, by using linear PCA. 
This results into usable bounds, allowing in real time to certify robustness for $87\%$ of incoming images in the MNIST benchmark for a L1-perturbation of $\frac{1}{2}$, as well as for a surrogate computing the hidden plastic strain 
associated to a deformation map of a pipe.
	\end{abstract}

@@

	\input{introduction}
